%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Graduate Intern} % Job title
    {Interfront} % Organization
    {Somerset-West, Cape Town, South Africa} % Location
    { Feb. 2018 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented a tool in Scala that allows the Test Automation tool to read in GUI fields and easily test them. As an extension on that tool, implemented a python program that generates a given reports test suite. }
        \item {Implemented a visual comparison tool in Python using OpenCV and Scikit-learn. Used for comparing snapshots of GUI version and highlighting the differences to assist the Testing team for a more optimal GUI debugging.}
         \item {Build container views.}
              \item {Rebuilt Inbox app in new Angular 5 and also assisted in making the Inbox Back-end compatible with the new Stack.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Bursar Developer} % Job title
    {Interfront} % Organization
    {Somerset-West, Cape Town, South Africa} % Location
    {Dec. 2014 - Jan. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented RESTful API server using Java, Hibernate and spring as part of learning the Interfront way of work and technologies associated with it.}
        \item {Wrote protractor unit test for various GUI's for unit test automation.}
        \item {Assisted in the optimization and automation of the GUI build process by adding gulp scripts to libraries that weren't automated. Provided the documentation on how to use those various scripts. }
        \item {Did research in SDLC work-flow as part of a short time working with Business Analyst team to try and determine if an open-source application would fit within the Interfront SDLC.}
      \end{cvitems}
    }




%---------------------------------------------------------

\end{cventries}
